\documentclass[12pt]{article}


\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{marvosym}
\usepackage{graphicx}


\pagestyle{empty}

\usepackage[left=1in,top=0.5in,right=1in,bottom=0.5in]{geometry} % Document margins
\setlength{\parindent}{0pt}
\addtolength{\parskip}{6pt}

\def\firstname{Clarke}
\def\familyname{Iakovakis}
\def\FileAuthor{\firstname \familyname}
\def\FileTitle{\firstname \familyname's cover letter}
\def\FileSubject{Cover letter}
\def\FileKeyWords{\firstname \familyname, Cover letter}

\renewcommand{\ttdefault}{pcr}

\usepackage{url}
\urlstyle{tt}
\ifpdf
  \usepackage[pdftex,pdfborder=0,breaklinks,baseurl=http://,pdfpagemode=None,pdfstartview=XYZ,pdfstartpage=1]{hyperref}
  \hypersetup{
    pdfauthor   = \FileAuthor,%
    pdftitle    = \FileTitle,%
    pdfsubject  = \FileSubject,%
    pdfkeywords = \FileKeyWords,%
    pdfcreator  = \LaTeX,%
    pdfproducer = \LaTeX}
\else
  \usepackage[dvips]{hyperref}
\fi


\hypersetup{%
        colorlinks=true,
        citecolor={green},
        linkcolor={red},
        urlcolor={blue}}

\begin{document}

%---------------------------------------
% MY NAME AND ADDRESS
%---------------------------------------
%\sffamily   % for use with a résumé using sans serif fonts;
\rmfamily  % for use with a résumé using serif fonts;
\hfill%
\begin{minipage}[t]{.6\textwidth}
\raggedleft%
{\bfseries Clarke L. Iakovakis}\\
\small%
4205 Country Club Drive\\
Dickinson, TX  77539 \\
\Telefon~(512)296$\cdot$4686 \\
\Letter~\href{mailto:clarke.iakovakis@gmail.com}{clarke.iakovakis@gmail.com}
\end{minipage}\\

%---------------------------------------
% COMPANY ADDRESS
%---------------------------------------
\begin{minipage}[t]{.4\textwidth}
\raggedright%
{\bfseries Oklahoma State University}\\
\small %
Stillwater, OK 74078
\end{minipage}

\hfill
\today

\raggedright

Mr. Locy \& Members of the Hiring Committee,

I am writing to express my interest in the position of Assistant/Associate Professor \& Scholarly Services Librarian at the Edmon Low Library. I am a strong candidate for this position, with a graduate degree in information studies, extensive experience providing scholarly communications services, a professional dedication to open access, and active participation on the local, state, and national levels. I have ten years of employment in libraries, and over twenty years of employment in public service work.

I firmly believe librarians have the professional expertise to lead positive and important changes in the creation and dissemination of scholarship. As Scholarly Communications Librarian at the University of Houston-Clear Lake, I have helped to develop several formal scholarly communications services. Even before I formally assumed the position, I developed working relationships with deans, tenure \& promotion committees, and I have a proven record of successful collaboration to support critical needs in journal evaluation, impact metrics, author rights, and open access. 

I have presented numerous workshops to faculty on related topics, including ``Evaluating Your Research Impact,'' ``Understanding Altmetrics,'' \& ``Using the Publish or Perish software.'' This past semester, the Dean of the College of Business sought my help to develop a method for evaluating all journals faculty had published in for the last 5 years. I wrote scripts to harvest ISBNs, then merged the journal title list with Scimago and the Harzing Journal Quality List. This automation not only saved them a tremendous amount of time, it also gave them a rich set of journal-level metrics. I developed a three-part workshop series during Open Access Week 2017 on Open Access, Copyright \& Intellectual Property, and Open Data.

Recognizing the necessity of ensuring students' ETDs have a global reach, I led the university-wide transition from print to electronic theses and dissertations from the pilot project 2015 to full implementation in Fall 2017. As UHCL does not have a separate graduate school, I chaired the library committee that pitched the transition to the Provost, and I worked with library administration and staff to create internal procedures. I wrote format and submission policies, created Word templates, designed process flowcharts, and formed partnerships with deans, faculty, department chairs, and advising coordinators. I administer our Vireo instance, and have worked with technical services to develop metadata authority control in the Institutional Repository. I wrote a FAQ and template letter for students seeking permission to use copyrighted instruments, and I speak with all submitting doctoral students, allowing me to discuss open access, copyright, and embargoes, and offer research consultations and EndNote support. 

While I am excited by scholarly communications work, I also continue to enjoy many other aspects of librarianship. I assist with digital scholarship needs; for instance, using R to extract and analyze Tweets, working with Institutional Effectiveness staff to geocode student addresses and analyze them in ArcGIS, and helping students locate datasets and prepare them for analysis and visualization. I have worked thousands of hours at research consultation and circulation desks during the course of my career and have extensive experience providing reference services in all platforms. I have created curriculum and delivered information literacy sessions in numerous subject areas and for all levels, and I purchase materials to develop the collection. I continue to develop innovative workshops for students on R Programming and EndNote. My interest in data analysis and understanding collections usage has to collaboratations with technical services staff on several projects to clean bibliographic and vendor data, and create interactive visualizations of our collections intended to help liaisons make better-informed purchasing decisions. 

I am naturally inquisitive and have a number of professional interests. I serve on multiple library and shared governance university committees. I am current vice-chair on the planning committee for the Texas Conference on Digital Libraries, and a board member for the Texas ETD Association. This month, I am leading a three part webinar for ALCTS on \href{http://www.ala.org/alcts/confevents/upcoming/webinar/IntrotoR}{``Introduction to R For Libraries.''} I co-presented at ACRL 2017 on a \href{http://www.ala.org/acrl/sites/ala.org.acrl/files/content/conferences/confsandpreconfs/2017/IDontKnowWhatImLookingat.pdf}{usability study using eye tracking software}, and at ALA 2017 on \href{http://alcts.ala.org/news/2017/ac-personalizing-assessment/}{methods for personalizing collection assessment}. I have helped organize and lead a \href{http://clearlake2017.thatcamp.org/}{THATCamp} and multiple GIS Day events. I also remain engaged on an academic level, and am halfway through writing a thesis for a master's degree in history.

In sum, my demonstrated experience in the following areas makes me an excellent candidate for the Scholarly Services Librarian position:
\begin{itemize}
   \itemsep-0.25em \vspace{-1em} % Compress items in list together for aesthetics
	\item Dedication to library leadership in advocating for and implementing open access to student and faculty research
	\item Maintaining positive professional relationships with faculty, and providing services in all stages of the research lifecycle
	\item Participating and leading several library and university committees, working well in collaborative and team environments
	\item Using and teaching a range of digital scholarship, design, web, and research tools
	\item Energy, enthusiasm, and a passion for providing exceptional library services
\end{itemize}\vspace{-.5em}
I welcome the opportunity to contribute to your organization. Thank you for your consideration, and I look forward to hearing from you. \\[1em]

Sincerely,\\[2em] 
{\bfseries Clarke L. Iakovakis}

\end{document}